Binning Strategies and Related Loss for Large Data

### 2015-02-18 Paper.Rnw
Add quantile binning section to draft

>>>>

\subsection{Quantile Binning Algorithm}

We could also consider a quantile based binning algorithm where bin widths are adjusted such that each bin contains an equal proportion of the observed values. This is a fundimentally different approach than the standard and random binning algorithms defined previously where the goal was to display approximate density. This binning will not be considered for binning the data directly, but instead for further binning the initial bin counts for the purposes of rendering colors on a discrete color palette.

Suppose that we have values $c_j$ for $j \in \{1,2,...J\}$ that we wish to divide into quantile based bins. The number of quantile based bins, $N_q ,= J$ , must be defined in order to assign values to bin centers. The quantile binning function $b^q_C(\cdot)$ assigns ordered values $c_{(j)}$ to bin centers $c^\ast_{(j)}$ as 
%
\begin{eqnarray}\label{quantbin}
c^\ast_{(j)} = b^q_C(c_{(j)}) = c_{(\eta)} \text{, where } \eta = \left\lfloor j/ \left\lceil J/N_c \right\rceil \right\rfloor \left\lceil J/N_c \right\rceil ,
\end{eqnarray}
%
\noindent and $\left\lceil \cdot \right\rceil$ is the ceiling function that rounds any real number up to the next highest integer.  To better understand this function we notice that $\left\lceil J/N_c \right\rceil$ represents the number of values to be assigned to each quantile bin, $n_q$, rounded up; thus the function assigns the $j^{th}$ value to the next lower ordered value that is a multiple of $n_q$.
